Computer-supported Analysis of Modern Variants of G\"odel's Ontological Argument

### 2014-10-17 Papers/InProgress/LogicAndReligionCongress/Abstract.tex
draft update

We summarize the main results of our experiments, and we start with
Anderson's emendation (cf. Appendix \ref{apx:Anderson}), which we have
analysed for different domain conditions. These variations were
motivated by various comments on Anderson's work in the literature. 
\begin{itemize}
\item Constant domain semantics\footnote{Cf. Isabelle/HOL source file
    \url{Anderson/Anderson_constant_domain.thy}} (the individual
  domains remain the same in all worlds): G\"odel's theorems C1, and
  T3 can easily be automated (in logics K and KB, respectively) ,
  G\"odel's axioms A4 and A5 are proven redundant (the former one in
  logic K4B, the latter already in K); a trivial countermodel (two
  worlds, one individual; this is simpler than
          the countermodel with two individuals and two worlds
          presented by Anderson, 1990) to MC generated by Nitpick (for all mentioned
  logics); this model also proves consistency.
\item Varying domain semantics\footnote{Cf. Isabelle/HOL source file
    \url{Anderson/Anderson_varying_domain.thy}} (the domains for
  indivduals may vary from world to world, all other domains remain
  constant; different authors have pointed out that varying domain
  quantifiers should be used in Anderson's work; here we consistently
  used varying domain for all individual quantifiers; the varying
  domain quantifiers have been modeled by using an explicit
  ``Existence'' relation between indiviudals and worlds): we obtain
  the same results as  above
\item Mixed variant\footnote{Cf. Isabelle/HOL source file
    \url{Anderson/Anderson_mixed_domain.thy}} (varying domain
  quantifiers are used exclusively in the definitions of essence and
  NE; see the comments by Fitting): G\"odel's axioms A4 and A5 remain
  redundant (the former one in
  logic K4B, the latter already in K).
\end{itemize}

>>>>

We summarize the main results of our experiments, and we start with
Anderson's emendation (cf. Appendix \ref{apx:Anderson}), which we have
analysed for different domain conditions. These variations were
motivated by various comments on Anderson's work in the literature. 
\begin{itemize}
\item Constant domain semantics\footnote{Cf. Isabelle/HOL source file
    \url{Anderson/Anderson_constant_domain.thy}} (the individual
  domains remain the same in all worlds): G\"odel's theorems C1, and
  T3 can easily be automated (in logics K and KB, respectively) ,
  G\"odel's axioms A4 and A5 are proven redundant (the former one in
  logic K4B, the latter already in K); a trivial countermodel (two
  worlds, one individual; this is simpler than
          the countermodel with two individuals and two worlds
          presented by Anderson, 1990) to MC generated by Nitpick (for all mentioned
  logics); this model also proves consistency.
\item Varying domain semantics\footnote{Cf. Isabelle/HOL source file
    \url{Anderson/Anderson_varying_domain.thy}} (the domains for
  indivduals may vary from world to world, all other domains remain
  constant; different authors have pointed out that varying domain
  quantifiers should be used in Anderson's work; here we consistently
  used varying domain for all individual quantifiers; the varying
  domain quantifiers have been modeled by using an explicit
  ``Existence'' relation between indiviudals and worlds): we obtain
  the same results as  above
\item Mixed variant\footnote{Cf. Isabelle/HOL source files
    \url{Anderson/Anderson_mixed_domain_1/2.thy}} (varying domain
  quantifiers are used exclusively in the definitions of essence and
  NE; see the comments by Fitting): G\"odel's axioms A4 and A5 remain
  redundant (the former one in
  logic K4B, the latter already in K). The situation changes when only
  NE is modeled with a varying domain quantifier. Now, Nitpick reports
  a countermodel. 
\end{itemize}
